Monitoring and predictive mapping of floristic biodiversity along a climatic gradient in ENSO's terrestrial core region, NW Peru

### 2020-08-29 docs/enso_comp.Rmd
refine caption of table 1

```{r desc-stats, echo=FALSE}
div = readRDS(here("images/13_desc_stats_tab.rds"))
cap = paste("Different biodiversity measures across the studied years.",
            "min = minimum observed number of species per plot.",
            "max = maximum observed number of species per plot.")
kable(div, "latex", booktabs = TRUE, escape = TRUE, 
      # align = "c",
      # col.names = linebreak(nms, align = "c"),
      caption = cap)
```

>>>>

```{r desc-stats, echo=FALSE}
div = readRDS(here("images/13_desc_stats_tab.rds"))
cap = paste("Different biodiversity measures across the studied years.",
            "min = minimum observed number of species over all plots.",
            "max = maximum observed number of species over all plots.")
kable(div, "latex", booktabs = TRUE, escape = TRUE, 
      # align = "c",
      # col.names = linebreak(nms, align = "c"),
      caption = cap)
```
